---
title: "Master Thesis: data cleaning and wranggling"
author: "Óscar García Casanova"
date: "2023-07-15"
output:
  html_document:
    toc: true  # Add a table of contents
    toc_depth: 3  # Specify the depth of the TOC (adjust as needed)
---

Data cleaning and wrangling

Summary: The following R.Markdown script transforms the original CSES Module 5 Full Release dataset to enhance its readability and usability. To do so, it first renames the variables and codes missing values as such (Section 2, Data cleaning). Consequently, it generates derived variables from the ones available, to use in further analyses (Section 3, Data wrangling). At the end, only relevant analysis variables are elected and a new dataset df_nationalism is saved.
It is recommended to move through the script using the Outline buttom in the upper right corner of the R.Studio script visualization window, which contains all tasks numerated and defined.
In order to reset the source directory, it is recommended to use the Find/Replace tool from the upper toolbar, searching for "C:/Users/oscar/Documents/Projects/" and substituting for the adequate directory where the folder "Master Thesis - Oscar Garcia" is located
  
#1. Preparatory tasks
##1.a) Reset space and charge libraries

```{r, echo=FALSE}
rm(list=ls()) # Clean workspace
options(scipen=10000) # Set scientific notation
library(tidyverse)
library(factoextra) # For EFA
library(lavaan) # For CFA
library(semTools) # For measurement of invariance in MGCFA
```

##1.b) Open dataset 
The dataset can be retrieved in "https://cses.org/data-download/cses-module-5-2016-2021/" as a CSV.file

```{r}
df_nationalism <- read.csv("C:/Users/oscar/Documents/Projects/Master Thesis - Oscar Garcia/Quantitative Analysis/Data/cses5.csv", header = TRUE, sep = ",")
```

#2. Data cleaning: 
Task: coding variable names, coding NAs.

##2.a) List and change name for all variables of interest:

```{r}
df_nationalism$E2012 <- as.integer(df_nationalism$E2012)

df_nationalism <- df_nationalism %>%
  mutate(salfact1st = E5021_1, #    >>> MOST SALIENT FACTORS IN ELECTION - 1ST
         salfact2nd = E5021_2, #    >>> MOST SALIENT FACTORS IN ELECTION - 2ND
         salfact3rd = E5021_3, #    >>> MOST SALIENT FACTORS IN ELECTION - 3RD
         salfact4th = E5021_4, #    >>> MOST SALIENT FACTORS IN ELECTION - 4TH
         salfact5th = E5021_5, #    >>> MOST SALIENT FACTORS IN ELECTION - 5TH
         selfpleftright = E3020, 
         votleftcentrigh = E3013_LR_CSES, 
         countryyear = E1004,
         regioncode = E1006_REG, #
         countrycode = E1006_UNALPHA2, #
         countryname = E1006_NAM, #
         usapanel = E1009_P1,
         usapanelid = E1009_P2,
         eudummy = E1006_EU, #
         electionyear = E1008, #
         surveyyear = E1034,
         birthyear = E2001_Y, #
         gender = E2002, #
         edulvl = E2003, #
         maritalstts = E2004, #
         uniondummy = E2005, #
         employmentstts = E2006, #
         ocupation = E2007, #
         soceconstts = E2008, #
         pubprivempl = E2009, #
         quintinc = E2010, #
         inclvl = E2011, #
         householdnum = E2012, #
         religion = E2013, #
         relattendance = E2014, #
         race = E2015, #
         ethn = E2016, #
         birthcountry = E2017, #
         parentforeign = E2018, #
         langspoken = E2019, #
         regionres = E2020, #
         elecdistr = E2021, #
         ruralurban = E2022, #
         polinterest = E3001, #
         followmediapol = E3002, #
         understandpol = E3003, #
         atelcomprbad = E3004_1, #
         atelpeople = E3004_2, #
         atelpoltrust = E3004_3, #
         atelpolproblem = E3004_4, #
         atelstronglead = E3004_5, #
         atelpeopledec = E3004_6, #
         atelpolrichpow = E3004_7, #
         ougrcusttrad = E3005_1, #
         ougrmajwill = E3005_2, #
         econ_immig = E3005_3, #
         cult_immig = E3005_4, #
         sec_immig = E3005_5, #
         natidborncountr = E3006_1, #
         natidancestry = E3006_2, #
         natidspeaklang = E3006_3, #
         natidcusttrad = E3006_4, #
         corrwidespread = E3007, #
         govreduceincdif = E3008, #
         govperform = E3009, #
         partyreprdummy = E3010_1, #
         partyreprwhich = E3010_2, #
         econchng12m = E3011, #
         votednatelec = E3012, #
         votchoicepreel = E3013_PR_1, #
         votchoiceparel = E3013_LH_PL, #
         l2gini = E5092, #           >>>         GINI COEFFICIENT OF EQUALIZED DISPOSABLE INCOME
         l2inflationt0 = E5095_1, #  >>>         INFLATION, GDP DEFLATOR (ANNUAL %) (WORLD BANK) - TIME T
         l2inflationt1 = E5095_2, #  >>>         INFLATION, GDP DEFLATOR (ANNUAL %) (WORLD BANK) - TIME T-1
         l2inflationt2 = E5095_3, #  >>>         INFLATION, GDP DEFLATOR (ANNUAL %) (WORLD BANK) - TIME T-2
         l2gdpgrowtht0 = E5093_1, #  >>>         GDP GROWTH - ANNUAL % (WORLD BANK) - TIME T
         l2gdpgrowtht1 = E5093_2, #  >>>         GDP GROWTH - ANNUAL % (WORLD BANK) - TIME T-1
         l2gdpgrowtht2 = E5093_3, #  >>>         GDP GROWTH - ANNUAL % (WORLD BANK) - TIME T-2
         l2gdpcapt0 = E5094_1, #     >>>         GDP PER CAPITA, PPP (WORLD BANK) - TIME T
         l2gdpcapt1 = E5094_2, #     >>>         GDP PER CAPITA, PPP (WORLD BANK) - TIME T-1
         l2gdpcapt2 = E5094_3, #     >>>         GDP PER CAPITA, PPP (WORLD BANK) - TIME T-2
         l2hdit0 = E5097_1, #        >>>         HUMAN DEVELOPMENT INDEX (UNPD) - TIME T
         l2hdit1 = E5097_2, #        >>>         HUMAN DEVELOPMENT INDEX (UNPD) - TIME T-1
         l2hdit2 = E5097_3, #        >>>         HUMAN DEVELOPMENT INDEX (UNPD) - TIME T-2
         l2popt0 = E5098_1, #        >>>         POPULATION, TOTAL (WORLD BANK) - TIME T
         l2popt1 = E5098_2, #        >>>         POPULATION, TOTAL (WORLD BANK) - TIME T-1
         l2popt2 = E5098_3, #        >>>         POPULATION, TOTAL (WORLD BANK) - TIME T-2
         l2unemplt0 = E5099_1, #     >>>         UNEMPLOYMENT, TOTAL (WORLD BANK) - TIME T
         l2unemplt1 = E5099_2, #     >>>         UNEMPLOYMENT, TOTAL (WORLD BANK) - TIME T-1
         l2unemplt2 = E5099_3, #     >>>         UNEMPLOYMENT, TOTAL (WORLD BANK) - TIME T-2
         l2youngunemt0 = E5100_1, #  >>>         UNEMPLOYMENT, TOTAL FOR PEOPLE AGED 15-24 YEARS (WORLD BANK) - TIME T
         l2youngunemt1 = E5100_2, #  >>>         UNEMPLOYMENT, TOTAL FOR PEOPLE AGED 15-24 YEARS (WORLD BANK) - TIME T-1
         l2youngunemt2 = E5100_3, #  >>>         UNEMPLOYMENT, TOTAL FOR PEOPLE AGED 15-24 YEARS (WORLD BANK) - TIME T-2
         l2imfdummy = E5101, #       >>>         COUNTRY SUBJECT TO IMF CONDITIONALITY AT ELECTION
         l2corrupperc = E5102, #     >>>         TI CORRUPTION PERCEPTION INDEX
         l2corrup0 = E5103_1, #      >>>         CONTROL OF CORRUPTION INDEX - TIME T
         l2corrse0 = E5103_1se, #    >>>         CONTROL OF CORRUPTION INDEX - TIME T STANDARD ERROR
         l2corrupt1 = E5103_2, #     >>>         CONTROL OF CORRUPTION INDEX - TIME T-1
         l2corrset1 = E5103_2se, #   >>>         CONTROL OF CORRUPTION INDEX - TIME T-1 STANDARD ERROR
         l2corrupt2 = E5103_3, #        >>>         CONTROL OF CORRUPTION INDEX - TIME T-2
         l2corrset2 = E5103_3se, #      >>>         CONTROL OF CORRUPTION INDEX - TIME T-2 STANDARD ERROR)
         codecountrystudy = E1006_UN) #      >>>         COUNTRY OF STUDY; 3-DIGITS NUMERIC CODE
```

##2.b) Set missing cases for all variables of interest
###2.b) 1.- Code to set value 9999 as missing value for election and survey years
```{r}
df_nationalism <- df_nationalism %>% 
  mutate(electionyear = ifelse(electionyear %in% c(9999), NA, electionyear))

```

```{r}
df_nationalism <- df_nationalism %>% 
  mutate(surveyyear = ifelse(surveyyear %in% c(9999), NA, surveyyear))

```

###2.b) 2.- Code to set values 9997, 9998 and 9999 as missing value
```{r}
df_nationalism <- df_nationalism %>% 
  mutate(birthyear = ifelse(birthyear %in% c(9997, 9998, 9999), NA, birthyear))
```

###2.b) 3.- Code to set values 7, 8 and 9 as missing values
```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(c(votleftcentrigh,
                  gender,
                  maritalstts,
                  uniondummy,
                  soceconstts,
                  pubprivempl,
                  quintinc, 
                  parentforeign, 
                  ruralurban,
                  relattendance,
                  polinterest,
                  followmediapol,
                  understandpol,
                  atelcomprbad,
                  atelpeople,
                  atelpoltrust,
                  atelpolproblem,
                  atelstronglead,
                  atelpeopledec,
                  atelpolrichpow,
                  ougrcusttrad,
                  ougrmajwill,
                  econ_immig,
                  cult_immig,
                  sec_immig,
                  natidborncountr,
                  natidancestry,
                  natidspeaklang,
                  natidcusttrad,
                  corrwidespread,
                  govperform,
                  partyreprdummy,
                  econchng12m), 
                ~ifelse(. %in% c(7, 8, 9), NA, .)))
```

###2.b) 4.- Code to set values 4 and 5 for pubprivempl as missing values

```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(pubprivempl,
                ~ifelse(. %in% c(4, 5), NA, .)))
```

###2.b) 5.- Code to set values 6 (wrong observations in Belgium) for govperform as missing values

```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(govperform,
                ~ifelse(. %in% c(6), NA, .)))
```

###2.b) 6.- Code to set values 999988, 999989, 999990, 999991, 999992, 999993, 999995, 999996, 999997, 999998 and 999999 as missing values:

```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(c(votchoiceparel,
                  votchoicepreel), 
                ~ifelse(. %in% c(999988, 999989, 999990, 999991, 999992, 999993, 999995, 999996, 999997, 999998, 999999), NA, .)))
```

###2.b) 7.- Code to set values 97, 98 and 99 as missing values:

```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(c(E5020_A,
                  E5020_B,
                  E5020_C,
                  E5020_D,
                  E5020_E,
                  E5020_F,
                  E5020_G,
                  E5020_H,
                  E5020_I,
                  edulvl,
                  selfpleftright), 
                ~ifelse(. %in% c(95, 96, 97, 98, 99), NA, .)))
```

###2.b) 8.- Code to set values 99999 missing
```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(c(l2inflationt0,
                  l2inflationt1,
                  l2inflationt2), 
                ~ifelse(. %in% c(99999), NA, .)))
```

###2.b) 9.- Code to set values 999 missing
```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(c(l2hdit0,
                  l2hdit1,
                  l2hdit2), 
                ~ifelse(. %in% c(999), NA, .)))
```

###2.b) 9.- Code to set values 99999999999 and 99999999997 as missing
```{r}
df_nationalism <- df_nationalism %>% 
  mutate(across(c(usapanelid), 
                ~ifelse(. %in% c(99999999999, 99999999997), NA, .)))
```

#3. Data wranggling
##3.a) Create new variable immigrant

```{r}
# Create immigrant variable
df_nationalism <- df_nationalism %>%
  mutate(immigrant = ifelse(codecountrystudy == birthcountry, 1, 0))
```


##3.a) Reverse variables to follow desired order based upon research question 
###3.a) 1.- Reverse specific attitudinal values to make them follow same order:

```{r}

df_nationalism <- df_nationalism %>%
  mutate(atelpoldistrust = 6 - atelpoltrust,
         econ_immig = 6 - econ_immig,
         natidborncountr = 5 - natidborncountr,
         natidancestry = 5 - natidancestry,
         natidspeaklang = 5 - natidspeaklang,
         natidcusttrad = 5 - natidcusttrad)

```

###3.a) 2.- Reverse ruralurban variable to make it grow with rural, thus easier to read

```{r}

df_nationalism <- df_nationalism %>%
  mutate(urbanrural = 5 - ruralurban)
```

##3.b) Create new variables:
###3.b) 1.- Create age and agerange variables:

```{r}
df_nationalism <- df_nationalism %>%
  mutate(age = surveyyear - birthyear)

df_nationalism <- df_nationalism %>%
  mutate(agerange = case_when(
    age >= 0 & age <= 20 ~ 1,
    age > 20 & age <= 25 ~ 2,
    age > 25 & age <= 30 ~ 3,
    age > 30 & age <= 35 ~ 4,
    age > 35 & age <= 40 ~ 5,
    age > 40 & age <= 45 ~ 6,
    age > 45 & age <= 50 ~ 7,
    age > 50 & age <= 55 ~ 8,
    age > 55 & age <= 60 ~ 9,
    age > 60 & age <= 65 ~ 10,
    age > 65 & age <= 70 ~ 11,
    age > 70 & age <= 75 ~ 12,
    age > 75 & age <= 80 ~ 13,
    age > 80 & age <= 100 ~ 14,
    TRUE ~ NA_real_
))

```

###3.b) 2.- Create generation variable

```{r}
df_nationalism <- df_nationalism %>%
  mutate(generation = case_when(
    birthyear <= 1927 ~ "Greatest generation: < 1927",
    between(birthyear, 1928, 1945) ~ "Silent generation: 1928 - 1945",
    between(birthyear, 1946, 1964) ~ "Baby boomers: 1946 - 1964",
    between(birthyear, 1965, 1980) ~ "Generation X: 1965 - 1980",
    between(birthyear, 1981, 1996) ~ "Generation Y: 1981 - 1996",
    birthyear >= 1997 ~ "Generation Z: > 1997",
    TRUE ~ NA_character_  # Handle missing or invalid values
  ))

```


###3.b) 3.- Create votechoice string variable for both party voted for lower camera (parliament) and person/party voted for presidential office:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(votchoiceparstr = as.character(votchoiceparel))%>%
  mutate(votchoiceprestr = as.character(votchoicepreel))

```

###3.b) 4.- Create populistlvlvote variable showing position of party voted for lower camera (parliament) or party/person voted for presidential office in populism scale:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(populistlvlvote = ifelse(!is.na(votchoiceprestr),
                                  ifelse(grepl("001", votchoiceprestr), E5020_A,
                                         ifelse(grepl("002", votchoiceprestr), E5020_B,
                                                ifelse(grepl("003", votchoiceprestr), E5020_C,
                                                       ifelse(grepl("004", votchoiceprestr), E5020_D,
                                                              ifelse(grepl("005", votchoiceprestr), E5020_E,
                                                                     ifelse(grepl("006", votchoiceprestr), E5020_F,
                                                                            ifelse(grepl("007", votchoiceprestr), E5020_G,
                                                                                   ifelse(grepl("008", votchoiceprestr), E5020_H,
                                                                                          ifelse(grepl("009", votchoiceprestr), E5020_I, NA))))))))),
                                  ifelse(grepl("001", votchoiceparstr), E5020_A,
                                         ifelse(grepl("002", votchoiceparstr), E5020_B,
                                                ifelse(grepl("003", votchoiceparstr), E5020_C,
                                                       ifelse(grepl("004", votchoiceparstr), E5020_D,
                                                              ifelse(grepl("005", votchoiceparstr), E5020_E,
                                                                     ifelse(grepl("006", votchoiceparstr), E5020_F,
                                                                            ifelse(grepl("007", votchoiceparstr), E5020_G,
                                                                                   ifelse(grepl("008", votchoiceparstr), E5020_H,
                                                                                          ifelse(grepl("009", votchoiceparstr), E5020_I, NA)))))))))))

df_nationalism <- df_nationalism %>%
  mutate(populistlvlvote = populistlvlvote/10)

```

###3.b) 5.- Create index of populist attitudes (based upon indicated reference), antielitism, outer group, immigration and national identity attitudinal items, then reverse new variables so that higher equals more populism:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(pop_att = (atelcomprbad+((atelpeople+atelpoldistrust+atelpolproblem+atelpolrichpow)/4)+atelpeopledec)/3) %>%
  mutate(antielitism = (atelcomprbad + atelpeople + atelpoldistrust + atelpolproblem + atelstronglead + atelpeopledec + atelpolrichpow)/7) %>%
  mutate(outergroup = (ougrcusttrad + ougrmajwill + econ_immig + cult_immig + sec_immig)/5) %>%
  mutate(nationalidentity = (natidborncountr + natidancestry + natidspeaklang + natidcusttrad)/4) #%>%
  #mutate(perc_immig_effect  = (econ_immig + cult_immig + sec_immig)/3)

# Calculate the reversed values for the three variables
df_nationalism <- df_nationalism %>%
  mutate(pop_att = 6 - pop_att,
         antielitism = 6 - antielitism,
         outergroup = 6 - outergroup,
         nationalidentity = 6 - nationalidentity)
```

###3.b) 6.- Create variable dummy agricultural vs. non-agricultural work:
```{r}
# Create a dummy variable based on soceconstts with specific values using pipe operators
df_nationalism <- df_nationalism %>%
  mutate(farmerdummy = case_when(
    soceconstts == 3 ~ "Farmer",
    soceconstts %in% c(1, 2, 4, 5) ~ "No farmer",
    TRUE ~ NA_character_
  ))

```

###3.b) 7.- Create variable dummy Western vs. Eastern (aka post-soviet space) Europe:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(westeastdummy = case_when(
    countryname == "Lithuania" ~ 1,
    countryname == "Montenegro" ~ 1,
    regioncode %in% c(155, 39, 154) ~ 0,
    regioncode == 151 ~ 1,
    TRUE ~ NA_real_
  ))

```

###3.b) 8.- Create inflation before the elections weighted as 50 t0, 33 t-1 and 17 t-2:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(l2winflationT3 = (l2inflationt0*0.5)+(l2inflationt1*0.33)+(l2inflationt2*0.17))

```

###3.b) 9.- Create GDP growth before the elections weighted as 50 t0, 33 t-1 and 17 t-2:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(l2gdpgrowthT3 = (l2gdpgrowtht0*50)+(l2gdpgrowtht1*33)+(l2gdpgrowtht2*17))

```

###3.b) 10.- Create GDP per Capita before the elections weighted as 50 t0, 33 t-1 and 17 t-2:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(l2gdpcapT3 = (l2gdpcapt0*50)+(l2gdpcapt1*33)+(l2gdpcapt2*17))

```

###3.b) 11.- Create Human Developmemt Index change t0-t-2:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(l2hdievolT3 = l2hdit0-l2hdit2)

```

###3.b) 12.- Create unemployment before the elections weighted as 50 t0, 33 t-1 and 17 t-2:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(l2unemplT3 = (l2unemplt0*50)+(l2unemplt1*33)+(l2unemplt2*17))

```

###3.b) 13.- Create young unemployment before the elections weighted as 50 t0, 33 t-1 and 17 t-2:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(l2youngunemT3 = (l2youngunemt0*50)+(l2youngunemt1*33)+(l2youngunemt2*17))

```

###3.b) 14.- Create areaname: convert regioncode in string variable and transforming number codes into the corresponding geographic categories, then create superior level areaname:
```{r}
df_nationalism <- df_nationalism %>%
  mutate(regioncode = as.character(regioncode))
```

```{r}
df_nationalism <- df_nationalism %>%
  mutate(regioncode = case_when(
    regioncode == "14" ~ "Eastern Africa",
    regioncode == "15" ~ "Northern Africa",
    regioncode == "18" ~ "Southern Africa",
    regioncode == "5" ~ "South America",
    regioncode == "21" ~ "North America",
    regioncode == "13" ~ "Central America",
    regioncode == "151" ~ "Eastern Europe",
    regioncode == "39" ~ "Southern Europe",
    regioncode == "154" ~ "Northern Europe",
    regioncode == "155" ~ "Western Europe",
    regioncode == "30" ~ "Eastern Asia",
    regioncode == "35" ~ "South Eastern Asia",
    regioncode == "143" ~ "Central Asia",
    regioncode == "145" ~ "Western Asia",
    regioncode == "9" ~ "Oceania",
    TRUE ~ NA_character_
  ))%>%
  mutate(areaname = case_when(
    regioncode %in% c("Eastern Africa", "Northern Africa", "Southern Africa") ~ "Africa",
    regioncode %in% c("South America", "Central America") ~ "Latin America",
    regioncode %in% c("North America") ~ "North America",
    regioncode %in% c("Eastern Europe", "Southern Europe", "Northern Europe", "Western Europe") ~ "Europe",
    regioncode %in% c("Eastern Asia", "South Eastern Asia", "Central Asia", "Western Asia") ~ "Asia",
    regioncode %in% c("Oceania") ~ "Oceania",
    TRUE ~ NA_character_
  ))

```

###3.b) 15.- Create variable left-wing / center / right-wing:

```{r}
df_nationalism <- df_nationalism %>%
  mutate(leftrightdummy = case_when(
    between(selfpleftright, 0, 4) ~ "0. Left",
    between(selfpleftright, 5, 5) ~ "1. Center",
    between(selfpleftright, 6, 10) ~ "2. Right",
    TRUE ~ NA_character_
  ))

```

###3.b) 16.- Create categorical left-right wing variable

```{r}
df_nationalism <- df_nationalism %>%
  mutate(leftright_cat = case_when(
    between(selfpleftright, 0, 2) ~ "Extreme Left",
    between(selfpleftright, 3, 4) ~ "Center Left",
    between(selfpleftright, 5, 5) ~ "Center",
    between(selfpleftright, 6, 7) ~ "Center Right",
    between(selfpleftright, 8, 10) ~ "Extreme Right",
    TRUE ~ NA_character_
  ))

```


###3.b) 16.- Put characters into region code

```{r}
df_nationalism <- df_nationalism %>%
  mutate(regioncode = case_when(
    regioncode == "14" ~ "Eastern Africa",
    regioncode == "15" ~ "Northern Africa",
    regioncode == "18" ~ "Southern Africa",
    regioncode == "5" ~ "South America",
    regioncode == "21" ~ "North America",
    regioncode == "13" ~ "Central America",
    regioncode == "151" ~ "Eastern Europe",
    regioncode == "39" ~ "Southern Europe",
    regioncode == "154" ~ "Northern Europe",
    regioncode == "155" ~ "Western Europe",
    regioncode == "30" ~ "Eastern Asia",
    regioncode == "35" ~ "South Eastern Asia",
    regioncode == "143" ~ "Central Asia",
    regioncode == "145" ~ "Western Asia",
    regioncode == "9" ~ "Oceania",
    TRUE ~ NA_character_
  ))

```

###3.b) 17.- Reorganize gender [0=male, 1=female]
```{r}
df_nationalism <- df_nationalism %>%
  mutate(gender = case_when(
    gender == 1 ~ 0,
    gender == 2 ~ 1,
    TRUE ~ NA_real_
  ))

```

###3.b) 18.- Create higher level religion

```{r}
df_nationalism <- df_nationalism %>%
  mutate(religion_gen = recode(religion,
    `1000` = "Christian",
    `1101` = "Catholic",
    `1102` = "Catholic",
    `1199` = "Catholic",
    `1200` = "Protestant",
    `1201` = "Protestant",
    `1203` = "Protestant",
    `1204` = "Protestant",
    `1205` = "Protestant",
    `1206` = "Protestant",
    `1207` = "Protestant",
    `1208` = "Protestant",
    `1209` = "Protestant",
    `1210` = "Protestant",
    `1211` = "Protestant",
    `1212` = "Protestant",
    `1213` = "Protestant",
    `1214` = "Protestant",
    `1215` = "Protestant",
    `1216` = "Protestant",
    `1217` = "Protestant",
    `1298` = "Protestant",
    `1299` = "Protestant",
    `1300` = "Anglican",
    `1401` = "Independents-Non-Affiliated",
    `1410` = "Independents-Non-Affiliated",
    `1420` = "Independents-Non-Affiliated",
    `1499` = "Independents-Non-Affiliated",
    `1501` = "Non-Traditional Protestants",
    `1502` = "Non-Traditional Protestants",
    `1503` = "Non-Traditional Protestants",
    `1504` = "Non-Traditional Protestants",
    `1599` = "Non-Traditional Protestants",
    `1600` = "Orthodox",
    `1698` = "Orthodox",
    `1699` = "Orthodox",
    `2000` = "Jewish",
    `3000` = "Islam",
    `3100` = "Islam",
    `3200` = "Islam",
    `3210` = "Islam",
    `3211` = "Islam",
    `4000` = "Buddhism",
    `4100` = "Buddhism",
    `4200` = "Buddhism",
    `5000` = "Hinduism and Other Religions of India",
    `5010` = "Hinduism and Other Religions of India",
    `5020` = "Hinduism and Other Religions of India",
    `5030` = "Hinduism and Other Religions of India",
    `5040` = "Hinduism and Other Religions of India",
    `5500` = "Hinduism and Other Religions of India",
    `5600` = "Hinduism and Other Religions of India",
    `6100` = "Indigenous Religions of East Asia",
    `6200` = "Indigenous Religions of East Asia",
    `6300` = "Indigenous Religions of East Asia",
    `6400` = "Indigenous Religions of East Asia",
    `6401` = "Indigenous Religions of East Asia",
    `6500` = "Indigenous Religions of East Asia",
    `7100` = "Ethnoreligions/Other Believer",
    `7110` = "Ethnoreligions/Other Believer",
    `7200` = "Ethnoreligions/Other Believer",
    `7500` = "Ethnoreligions/Other Believer",
    `7900` = "Ethnoreligions/Other Believer",
    `7901` = "Ethnoreligions/Other Believer",
    `8100` = "Non Believers",
    `8200` = "Non Believers",
    `8300` = "Non Believers"
  ))

```

###3.b) 19.- Create higher level ocupation

```{r}
df_nationalism <- df_nationalism %>%
  mutate(ocupation_gen = recode(ocupation,
    "00" = "Armed Forces Occupations",
    "01" = "Armed Forces Occupations",
    "02" = "Armed Forces Occupations",
    "03" = "Armed Forces Occupations",
    "10" = "Managers",
    "11" = "Managers",
    "12" = "Managers",
    "13" = "Managers",
    "14" = "Managers",
    "20" = "Professionals",
    "21" = "Professionals",
    "22" = "Professionals",
    "23" = "Professionals",
    "24" = "Professionals",
    "25" = "Professionals",
    "26" = "Professionals",
    "30" = "Technicians and associate professionals",
    "31" = "Technicians and associate professionals",
    "32" = "Technicians and associate professionals",
    "33" = "Technicians and associate professionals",
    "34" = "Technicians and associate professionals",
    "35" = "Technicians and associate professionals",
    "40" = "Clerical Support Workers",
    "41" = "Clerical Support Workers",
    "42" = "Clerical Support Workers",
    "43" = "Clerical Support Workers",
    "44" = "Clerical Support Workers",
    "50" = "Service and Sales Workers",
    "51" = "Service and Sales Workers",
    "52" = "Service and Sales Workers",
    "53" = "Service and Sales Workers",
    "54" = "Service and Sales Workers",
    "60" = "Skilled Agricultural, Forestry and Fishery Workers",
    "61" = "Skilled Agricultural, Forestry and Fishery Workers",
    "62" = "Skilled Agricultural, Forestry and Fishery Workers",
    "63" = "Skilled Agricultural, Forestry and Fishery Workers",
    "70" = "Craft and Related Trades Workers",
    "71" = "Craft and Related Trades Workers",
    "72" = "Craft and Related Trades Workers",
    "73" = "Craft and Related Trades Workers",
    "74" = "Craft and Related Trades Workers",
    "75" = "Craft and Related Trades Workers",
    "80" = "Plant and Machine Operators, and Assemblers",
    "81" = "Plant and Machine Operators, and Assemblers",
    "82" = "Plant and Machine Operators, and Assemblers",
    "83" = "Plant and Machine Operators, and Assemblers",
    "90" = "Elementary Occupations",
    "91" = "Elementary Occupations",
    "92" = "Elementary Occupations",
    "93" = "Elementary Occupations",
    "94" = "Elementary Occupations",
    "95" = "Elementary Occupations",
    "96" = "Elementary Occupations"
  ))

```
###3.b) 20.- Create text variable of employmentstts

```{r}
# Apply the transformation to df_nationalism
df_nationalism <- df_nationalism %>%
  mutate(
    employmentstts_string = case_when(
      employmentstts == 1 ~ "Employed - Full-time (32 or more hours weekly)",
      employmentstts == 2 ~ "Employed - Part-time (15-32 hours weekly)",
      employmentstts == 3 ~ "Employed - Less than 15 hours",
      employmentstts == 4 ~ "Helping Family Member",
      employmentstts == 5 ~ "Unemployed",
      employmentstts == 6 ~ "Student, in School, in Vocational Training",
      employmentstts == 7 ~ "Retired",
      employmentstts == 8 ~ "Housewife, Home Duties",
      employmentstts == 9 ~ "Permanently Disabled",
      employmentstts == 10 ~ "Others, Not in Labor Force",
      employmentstts == 11 ~ "On Temporary Job Leave (Maternity Leave, Sick Leave, etc.)",
      employmentstts == 12 ~ "Civil / Military Service",
      TRUE ~ "Unknown"  # Handle any other values not in the mapping
    )
  )
```


#4. Final procedures
##4.a) Select only possibly useful variables variables:

```{r}
df_nationalism <- df_nationalism %>%
  select(c(salfact1st, #    >>> MOST SALIENT FACTORS IN ELECTION - 1ST
           salfact2nd, #    >>> MOST SALIENT FACTORS IN ELECTION - 2ND
           salfact3rd, #    >>> MOST SALIENT FACTORS IN ELECTION - 3RD
           salfact4th, #    >>> MOST SALIENT FACTORS IN ELECTION - 4TH
           salfact5th,
           countryyear,
           usapanelid,
           usapanel,
           maritalstts,
           generation, 
           employmentstts_string,
           leftright_cat,
           ocupation_gen,
           ocupation,
           religion_gen,
           religion,
           relattendance,
           parentforeign,
           leftrightdummy,
           areaname,
           selfpleftright, 
           votleftcentrigh,
           electionyear,
           l2youngunemT3,
           l2gdpgrowthT3, 
           l2gdpcapT3,
           l2hdievolT3, 
           l2hdit0,
           l2unemplT3, 
           l2winflationT3,
           l2gini, 
           farmerdummy,
           populistlvlvote,
           age,
           agerange,
           westeastdummy,
           countryname,
           votchoiceprestr,
           votchoiceparstr,
           regioncode,
           eudummy,
           edulvl,
           urbanrural,
           pop_att,
           antielitism,
           outergroup,
           nationalidentity,
           gender,
           maritalstts,
           uniondummy,
           soceconstts,
           pubprivempl,
           quintinc, 
           parentforeign,
           relattendance,
           polinterest,
           followmediapol,
           understandpol,
           atelcomprbad,
           atelpeople,
           atelpoldistrust,
           atelpolproblem,
           atelstronglead,
           atelpeopledec,
           atelpolrichpow,
           ougrcusttrad,
           ougrmajwill,
           econ_immig,
           cult_immig,
           sec_immig,
           natidborncountr,
           natidancestry,
           natidspeaklang,
           natidcusttrad,
           corrwidespread,
           govperform,
           partyreprdummy,
           econchng12m,
           immigrant
           ))
```

##4.b) Create unique study var countrynameyear, l2 identifier

```{r}
# Generate the new variable countrynameyear
df_nationalism <- df_nationalism %>%
  mutate(countrynameyear = paste(countryname, as.character(electionyear), sep = "_"))

```

##4.c) Save clean dataset:

```{r}
write.csv(df_nationalism, file = "C:/Users/oscar/Documents/Projects/Master Thesis - Oscar Garcia/Quantitative Analysis/Data/df_nationalism.csv", row.names = FALSE)
```
